Generating Random Logic Programs Using Constraint Programming

### 2020-04-19 paper2/impact.tex
Second publication attempt

% Created by tikzDevice version 0.12.3 on 2020-01-22 11:34:15
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (216.81,176.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (216.81,176.16);
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{255,255,255}

@@

\path[] (198.49, 79.68) -- (188.26, 77.20);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.83) --
	(210.30, 74.83) --
	(210.23, 74.83) --
	(210.52, 74.84) --
	(210.80, 74.90) --
	(211.07, 75.00) --
	(211.33, 75.15) --
	(211.55, 75.33) --
	(211.74, 75.55) --
	(211.90, 75.80) --
	(212.01, 76.06) --
	(212.08, 76.35) --
	(212.11, 76.63) --
	(212.11, 76.63) --
	(212.11, 82.96) --
	(212.11, 82.96) --
	(212.08, 83.25) --
	(212.01, 83.54) --
	(211.90, 83.80) --
	(211.74, 84.05) --
	(211.55, 84.27) --
	(211.33, 84.45) --
	(211.07, 84.60) --
	(210.80, 84.70) --
	(210.52, 84.76) --
	(210.30, 84.77) --
	(200.30, 84.77) --
	(200.52, 84.76) --
	(200.23, 84.77) --
	(199.94, 84.73) --
	(199.66, 84.65) --
	(199.40, 84.53) --
	(199.16, 84.36) --
	(198.95, 84.16) --
	(198.77, 83.93) --
	(198.64, 83.67) --
	(198.55, 83.40) --
	(198.50, 83.11) --
	(198.49, 82.96) --
	(198.49, 76.63) --
	(198.50, 76.78) --
	(198.50, 76.49) --
	(198.55, 76.20) --
	(198.64, 75.93) --
	(198.77, 75.67) --
	(198.95, 75.44) --
	(199.16, 75.24) --
	(199.40, 75.07) --
	(199.66, 74.95) --
	(199.94, 74.86) --
	(200.23, 74.83) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.84) {$|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (198.97, 67.62) -- (188.26, 70.73);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.43) --
	(210.30, 62.43) --
	(210.23, 62.43) --
	(210.52, 62.44) --
	(210.80, 62.50) --
	(211.07, 62.60) --
	(211.33, 62.75) --
	(211.55, 62.93) --
	(211.74, 63.15) --
	(211.90, 63.39) --
	(212.01, 63.66) --
	(212.08, 63.94) --
	(212.11, 64.23) --
	(212.11, 64.23) --
	(212.11, 70.56) --
	(212.11, 70.56) --
	(212.08, 70.85) --
	(212.01, 71.13) --
	(211.90, 71.40) --
	(211.74, 71.65) --
	(211.55, 71.87) --
	(211.33, 72.05) --
	(211.07, 72.19) --
	(210.80, 72.30) --
	(210.52, 72.36) --
	(210.30, 72.37) --
	(200.77, 72.37) --
	(200.99, 72.36) --
	(200.70, 72.37) --
	(200.41, 72.33) --
	(200.13, 72.25) --
	(199.87, 72.13) --
	(199.63, 71.96) --
	(199.42, 71.76) --
	(199.25, 71.53) --
	(199.11, 71.27) --
	(199.02, 71.00) --
	(198.97, 70.71) --
	(198.97, 70.56) --
	(198.97, 64.23) --
	(198.97, 64.38) --
	(198.97, 64.09) --
	(199.02, 63.80) --
	(199.11, 63.53) --
	(199.25, 63.27) --
	(199.42, 63.04) --
	(199.63, 62.83) --
	(199.87, 62.67) --
	(200.13, 62.54) --
	(200.41, 62.46) --
	(200.70, 62.43) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{117,112,179}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.44) {$|\mathcal{V}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (199.59, 56.21) -- (188.26, 67.83);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.08) --
	(210.30, 50.08) --
	(210.23, 50.08) --
	(210.52, 50.10) --
	(210.80, 50.15) --
	(211.07, 50.26) --
	(211.33, 50.40) --
	(211.55, 50.59) --
	(211.74, 50.80) --
	(211.90, 51.05) --
	(212.01, 51.32) --
	(212.08, 51.60) --
	(212.11, 51.89) --
	(212.11, 51.89) --
	(212.11, 58.22) --
	(212.11, 58.22) --
	(212.08, 58.51) --
	(212.01, 58.79) --
	(211.90, 59.06) --
	(211.74, 59.30) --
	(211.55, 59.52) --
	(211.33, 59.71) --
	(211.07, 59.85) --
	(210.80, 59.95) --
	(210.52, 60.01) --
	(210.30, 60.02) --
	(201.40, 60.02) --
	(201.62, 60.01) --
	(201.33, 60.02) --
	(201.04, 59.99) --
	(200.76, 59.91) --
	(200.50, 59.78) --
	(200.26, 59.62) --
	(200.05, 59.42) --
	(199.87, 59.18) --
	(199.74, 58.93) --
	(199.65, 58.65) --
	(199.60, 58.36) --
	(199.59, 58.22) --
	(199.59, 51.89) --
	(199.60, 52.03) --
	(199.60, 51.74) --
	(199.65, 51.46) --
	(199.74, 51.18) --
	(199.87, 50.92) --
	(200.05, 50.69) --
	(200.26, 50.49) --
	(200.50, 50.32) --
	(200.76, 50.20) --
	(201.04, 50.12) --
	(201.33, 50.08) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{231,41,138}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.09) {$|\mathcal{C}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (189.92, 87.17) -- (188.26, 79.66);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.58, 87.17) --
	(203.32, 87.17) --
	(203.24, 87.17) --
	(203.53, 87.19) --
	(203.82, 87.24) --
	(204.09, 87.35) --
	(204.34, 87.49) --
	(204.57, 87.68) --
	(204.76, 87.89) --
	(204.92, 88.14) --
	(205.03, 88.41) --
	(205.10, 88.69) --
	(205.12, 88.98) --
	(205.12, 88.98) --
	(205.12, 95.31) --
	(205.12, 95.31) --
	(205.10, 95.60) --
	(205.03, 95.88) --
	(204.92, 96.15) --
	(204.76, 96.39) --
	(204.57, 96.61) --
	(204.34, 96.79) --
	(204.09, 96.94) --
	(203.82, 97.04) --
	(203.53, 97.10) --
	(203.32, 97.11) --
	(176.58, 97.11) --
	(176.79, 97.10) --
	(176.50, 97.11) --
	(176.21, 97.08) --
	(175.93, 97.00) --
	(175.67, 96.87) --
	(175.43, 96.71) --
	(175.22, 96.51) --
	(175.05, 96.27) --
	(174.91, 96.02) --
	(174.82, 95.74) --
	(174.77, 95.45) --
	(174.77, 95.31) --
	(174.77, 88.98) --
	(174.77, 89.12) --
	(174.77, 88.83) --
	(174.82, 88.55) --
	(174.91, 88.27) --
	(175.05, 88.01) --
	(175.22, 87.78) --
	(175.43, 87.58) --
	(175.67, 87.41) --
	(175.93, 87.29) --
	(176.21, 87.21) --
	(176.50, 87.17) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{102,166,30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.95, 90.18) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

@@

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (130.35, 75.50) --
	(143.54, 75.50) --
	(143.46, 75.51) --
	(143.75, 75.52) --
	(144.04, 75.58) --
	(144.31, 75.68) --
	(144.56, 75.82) --
	(144.79, 76.01) --
	(144.98, 76.23) --
	(145.14, 76.47) --
	(145.25, 76.74) --
	(145.32, 77.02) --
	(145.34, 77.31) --
	(145.34, 77.31) --
	(145.34, 83.64) --
	(145.34, 83.64) --
	(145.32, 83.93) --
	(145.25, 84.21) --
	(145.14, 84.48) --
	(144.98, 84.73) --
	(144.79, 84.94) --
	(144.56, 85.13) --
	(144.31, 85.27) --
	(144.04, 85.38) --
	(143.75, 85.43) --
	(143.54, 85.45) --
	(130.35, 85.45) --
	(130.57, 85.43) --
	(130.28, 85.44) --
	(129.99, 85.41) --
	(129.71, 85.33) --
	(129.45, 85.20) --
	(129.21, 85.04) --
	(129.00, 84.84) --
	(128.83, 84.61) --
	(128.69, 84.35) --
	(128.60, 84.07) --
	(128.55, 83.79) --
	(128.55, 83.64) --
	(128.55, 77.31) --
	(128.55, 77.46) --
	(128.55, 77.17) --
	(128.60, 76.88) --
	(128.69, 76.60) --
	(128.83, 76.35) --
	(129.00, 76.11) --
	(129.21, 75.91) --
	(129.45, 75.75) --
	(129.71, 75.62) --
	(129.99, 75.54) --
	(130.28, 75.51) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{217,95,2}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63,125.64) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03, 25.58) --
	( 25.78, 25.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03, 76.58) --
	( 25.78, 76.58);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 24.03,127.57) --
	( 25.78,127.57);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 34.30, 17.78) --
	( 34.30, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 85.62, 17.78) --
	( 85.62, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] (136.94, 17.78) --
	(136.94, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] (188.26, 17.78) --
	(188.26, 19.53);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
\definecolor{drawColor}{gray}{0.30}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-01-25 19:17:02
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (216.81,176.16);
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{gray}{0.92}

@@

\path[] (198.49, 79.80) -- (188.26, 77.20);
\definecolor{drawColor}{RGB}{27,158,119}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.30, 74.97) --
	(210.30, 74.97) --
	(210.23, 74.97) --
	(210.52, 74.98) --
	(210.80, 75.04) --
	(211.07, 75.14) --
	(211.33, 75.29) --
	(211.55, 75.47) --
	(211.74, 75.69) --
	(211.90, 75.94) --
	(212.01, 76.20) --
	(212.08, 76.49) --
	(212.11, 76.78) --
	(212.11, 76.78) --
	(212.11, 83.11) --
	(212.11, 83.11) --
	(212.08, 83.40) --
	(212.01, 83.68) --
	(211.90, 83.94) --
	(211.74, 84.19) --
	(211.55, 84.41) --
	(211.33, 84.59) --
	(211.07, 84.74) --
	(210.80, 84.84) --
	(210.52, 84.90) --
	(210.30, 84.91) --
	(200.30, 84.91) --
	(200.52, 84.90) --
	(200.23, 84.91) --
	(199.94, 84.88) --
	(199.66, 84.79) --
	(199.40, 84.67) --
	(199.16, 84.50) --
	(198.95, 84.30) --
	(198.77, 84.07) --
	(198.64, 83.81) --
	(198.55, 83.54) --
	(198.50, 83.25) --
	(198.49, 83.11) --
	(198.49, 76.78) --
	(198.50, 76.92) --
	(198.50, 76.63) --
	(198.55, 76.34) --
	(198.64, 76.07) --
	(198.77, 75.81) --
	(198.95, 75.58) --
	(199.16, 75.38) --
	(199.40, 75.21) --
	(199.66, 75.09) --
	(199.94, 75.01) --
	(200.23, 74.97) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{27,158,119}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.30, 77.98) {$|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (198.97, 67.74) -- (188.26, 70.73);
\definecolor{drawColor}{RGB}{117,112,179}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (200.77, 62.58) --
	(210.30, 62.58) --
	(210.23, 62.58) --
	(210.52, 62.59) --
	(210.80, 62.65) --
	(211.07, 62.75) --
	(211.33, 62.90) --
	(211.55, 63.08) --
	(211.74, 63.30) --
	(211.90, 63.54) --
	(212.01, 63.81) --
	(212.08, 64.09) --
	(212.11, 64.38) --
	(212.11, 64.38) --
	(212.11, 70.71) --
	(212.11, 70.71) --
	(212.08, 71.00) --
	(212.01, 71.29) --
	(211.90, 71.55) --
	(211.74, 71.80) --
	(211.55, 72.02) --
	(211.33, 72.20) --
	(211.07, 72.35) --
	(210.80, 72.45) --
	(210.52, 72.51) --
	(210.30, 72.52) --
	(200.77, 72.52) --
	(200.99, 72.51) --
	(200.70, 72.52) --
	(200.41, 72.48) --
	(200.13, 72.40) --
	(199.87, 72.28) --
	(199.63, 72.11) --
	(199.42, 71.91) --
	(199.25, 71.68) --
	(199.11, 71.42) --
	(199.02, 71.15) --
	(198.97, 70.86) --
	(198.97, 70.71) --
	(198.97, 64.38) --
	(198.97, 64.53) --
	(198.97, 64.24) --
	(199.02, 63.95) --
	(199.11, 63.68) --
	(199.25, 63.42) --
	(199.42, 63.19) --
	(199.63, 62.99) --
	(199.87, 62.82) --
	(200.13, 62.70) --
	(200.41, 62.61) --
	(200.70, 62.58) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{117,112,179}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.54, 65.59) {$|\mathcal{V}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (199.59, 56.31) -- (188.26, 67.83);
\definecolor{drawColor}{RGB}{231,41,138}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (201.40, 50.18) --
	(210.30, 50.18) --
	(210.23, 50.18) --
	(210.52, 50.19) --
	(210.80, 50.25) --
	(211.07, 50.35) --
	(211.33, 50.50) --
	(211.55, 50.68) --
	(211.74, 50.90) --
	(211.90, 51.15) --
	(212.01, 51.41) --
	(212.08, 51.70) --
	(212.11, 51.99) --
	(212.11, 51.99) --
	(212.11, 58.31) --
	(212.11, 58.31) --
	(212.08, 58.60) --
	(212.01, 58.89) --
	(211.90, 59.15) --
	(211.74, 59.40) --
	(211.55, 59.62) --
	(211.33, 59.80) --
	(211.07, 59.95) --
	(210.80, 60.05) --
	(210.52, 60.11) --
	(210.30, 60.12) --
	(201.40, 60.12) --
	(201.62, 60.11) --
	(201.33, 60.12) --
	(201.04, 60.08) --
	(200.76, 60.00) --
	(200.50, 59.88) --
	(200.26, 59.71) --
	(200.05, 59.51) --
	(199.87, 59.28) --
	(199.74, 59.02) --
	(199.65, 58.75) --
	(199.60, 58.46) --
	(199.59, 58.31) --
	(199.59, 51.99) --
	(199.60, 52.13) --
	(199.60, 51.84) --
	(199.65, 51.55) --
	(199.74, 51.28) --
	(199.87, 51.02) --
	(200.05, 50.79) --
	(200.26, 50.59) --
	(200.50, 50.42) --
	(200.76, 50.30) --
	(201.04, 50.22) --
	(201.33, 50.18) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{231,41,138}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (205.85, 53.19) {$|\mathcal{C}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

\path[] (189.67, 87.32) -- (188.26, 79.66);
\definecolor{drawColor}{RGB}{102,166,30}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (176.31, 87.32) --
	(203.05, 87.32) --
	(202.98, 87.32) --
	(203.27, 87.33) --
	(203.56, 87.39) --
	(203.83, 87.49) --
	(204.08, 87.64) --
	(204.31, 87.82) --
	(204.50, 88.04) --
	(204.65, 88.28) --
	(204.77, 88.55) --
	(204.84, 88.83) --
	(204.86, 89.12) --
	(204.86, 89.12) --
	(204.86, 95.45) --
	(204.86, 95.45) --
	(204.84, 95.74) --
	(204.77, 96.03) --
	(204.65, 96.29) --
	(204.50, 96.54) --
	(204.31, 96.76) --
	(204.08, 96.94) --
	(203.83, 97.09) --
	(203.56, 97.19) --
	(203.27, 97.25) --
	(203.05, 97.26) --
	(176.31, 97.26) --
	(176.53, 97.25) --
	(176.24, 97.26) --
	(175.95, 97.22) --
	(175.67, 97.14) --
	(175.41, 97.02) --
	(175.17, 96.85) --
	(174.96, 96.65) --
	(174.79, 96.42) --
	(174.65, 96.16) --
	(174.56, 95.89) --
	(174.51, 95.60) --
	(174.51, 95.45) --
	(174.51, 89.12) --
	(174.51, 89.27) --
	(174.51, 88.98) --
	(174.56, 88.69) --
	(174.65, 88.42) --
	(174.79, 88.16) --
	(174.96, 87.93) --
	(175.17, 87.72) --
	(175.41, 87.56) --
	(175.67, 87.44) --
	(175.95, 87.35) --
	(176.24, 87.32) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{102,166,30}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.57] at (189.68, 90.33) {$\mathcal{M}_{\mathcal{C}}-|\mathcal{P}|$};
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);

@@

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (130.35, 75.50) --
	(143.54, 75.50) --
	(143.46, 75.51) --
	(143.75, 75.52) --
	(144.04, 75.58) --
	(144.31, 75.68) --
	(144.56, 75.82) --
	(144.79, 76.01) --
	(144.98, 76.23) --
	(145.14, 76.47) --
	(145.25, 76.74) --
	(145.32, 77.02) --
	(145.34, 77.31) --
	(145.34, 77.31) --
	(145.34, 83.64) --
	(145.34, 83.64) --
	(145.32, 83.93) --
	(145.25, 84.21) --
	(145.14, 84.48) --
	(144.98, 84.72) --
	(144.79, 84.94) --
	(144.56, 85.13) --
	(144.31, 85.27) --
	(144.04, 85.37) --
	(143.75, 85.43) --
	(143.54, 85.45) --
	(130.35, 85.45) --
	(130.57, 85.43) --
	(130.28, 85.44) --
	(129.99, 85.41) --
	(129.71, 85.33) --
	(129.45, 85.20) --
	(129.21, 85.04) --
	(129.00, 84.84) --
	(128.83, 84.61) --
	(128.69, 84.35) --
	(128.60, 84.07) --
	(128.55, 83.78) --
	(128.55, 83.64) --
	(128.55, 77.31) --
	(128.55, 77.46) --
	(128.55, 77.17) --
	(128.60, 76.88) --
	(128.69, 76.60) --
	(128.83, 76.35) --
	(129.00, 76.11) --
	(129.21, 75.91) --
	(129.45, 75.75) --
	(129.71, 75.62) --
	(129.99, 75.54) --
	(130.28, 75.51) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 25.78, 19.53) rectangle (213.31,172.66);
\definecolor{drawColor}{RGB}{217,95,2}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.56] at ( 22.63,125.64) {4000};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (216.81,176.16);
\definecolor{drawColor}{gray}{0.30}
